---
title: "Query API"
output: 
  html_notebook:
    code_folding: none
---
Query the Metematics API with an self-created URL and save the output with different formats.

First you have to import the meteomatics module and the lubridate library

```{r}
library(lubridate)
library(MeteomaticsRConnector)
```

Input here your username and password from your meteomatics profile

```{r}
username <- "r-community"
password <- "Utotugode673"
```

Specify the output directory for your query.

```{r}
outputdir <- paste0(tempdir(), "/test_query.csv")

```

Input here the date and the time as class POSIXct.

```{r}
datetime <- strftime(ISOdatetime(year=as.integer(strftime(lubridate::today(),'%Y')),
                                 month=as.integer(strftime(lubridate::today(),'%m')),
                                 day=as.integer(strftime(lubridate::today(),'%d')),
                                 hour = 00, min = 00, sec = 00, tz = 'UTC'),
                     format = '%Y-%m-%dT%H:%M:%OSZ', tz = 'UTC')

```

Meteomatics provides an easy access to weather data in all formats via URL building. Explore our URL creator: https://www.meteomatics.com/en/api/url-creator/

```{r}
# In this example 2m temperature for today 00 UTC will be queried at location 52.520551,13.461804. The output file is set to csv.

url <- paste0(sprintf('https://%s:%s@api.meteomatics.com/', username, password),
                      datetime, '/t_2m:C/52.520551,13.461804/csv')
```


In the following, the request will start. If there is an error in the request as for example a wrong parameter or a date that doesn't exist, you get a message.

```{r}
data <- query_api(url, username, password, output_dir = outputdir)
```
This is further example for fetching temperature date, but now for the 800hPa level and in Kelvin units. The output from the Meteomatics Mix model is saved to a .json file.
```{r}
outputdir <- paste0(tempdir(), "/test_query.json")

url <- paste0(sprintf('https://%s:%s@api.meteomatics.com/', username, password),
                      datetime, '/t_800hPa:K/51.5073219,-0.1276474+47.4236,9.3622/json?model=mix')

query_api(url, username, password, output_dir = outputdir)

```

