---
title: "Grid as PNG"
output: 
  html_notebook:
    code_folding: none
---
Retrieve a grid from the Meteomatics Weather API and save it as png file


First you have to import the meteomatics module and the lubridate library

```{r}
library(lubridate)
library(MeteomaticsRConnector)
```

Input here your username and password from your meteomatics profile

```{r}
username <- "r-community"
password <- "Utotugode673"
```

Input here the name that your png-file should get.

```{r}
filepath <-  tempdir()
file1 <- paste0(filepath, "/grid_temperature_switzerland.png")
```
Input here the date and the time.

```{r}
datetime <- ISOdatetime(year = as.integer(strftime(lubridate::today(), '%Y')),
                        month = as.integer(strftime(lubridate::today(), '%m')),
                        day = as.integer(strftime(lubridate::today(), '%d')) - 1,
                        hour = 00, min = 00, sec = 00, tz = "UTC")
```

Choose the parameters and model you want to get and write them in the list. Check here which parameters are available: https://www.meteomatics.com/en/api/available-parameters/

```{r}
parameter <- "t_2m:C"
```

Input here the limiting coordinates of the extract you want to look at. You can also change the resolution.

```{r}
lat_N <- 48
lon_W <- 6
lat_S <- 45.5
lon_E <- 10.5

resolution <- "1200x800" 
# you can also use following resolution resolution <- "0.1,0.1"
```

Choose the model you want to query
```{r}
model <- "mix"
```

In the following, the request will start. If there is an error in the request as for example a wrong parameter or a date that doesn't exist, you get a message.

```{r}
query_grid_png(file1, datetime, parameter, lat_N, lon_W, lat_S, lon_E,
               resolution, username, password,
               model = model)
```

Your png file is now saved with the assigned name. If the picture is too small, make the resolution smaller. Hence, there are more points on the same distance and the picture gets bigger, but it also takes more time to generate the picture.

```{r}
library(knitr)
include_graphics(file1)

```



```{r}
file2 <- paste0(filepath, "/relative_humidity.png")

model <- "mix"


parameter <- "relative_humidity_2m:p"
lat_N <- 73
lon_W <- 0
lat_S <- 55
lon_E <- 35

resolution <- "1200x800"

query_grid_png(file2, datetime, parameter, lat_N, lon_W, lat_S, lon_E,
               resolution, username, password,
               model = model)
```
```{r}
include_graphics(file2)

```

