---
title: "Query timeseries for special locations"
output: 
  html_notebook:
    code_folding: none
---
Retrieve a time series from the Meteomatics Weather API


First you have to import the meteomatics module and the lubridate library

```{r}
library(lubridate)
library(MeteomaticsRConnector)
```

Input here your username and password from your meteomatics profile

```{r}
username <- "r-community"
password <- "Utotugode673"
```

Define a startdate and endddate as POSIXct class

```{r}
startdate <- as.POSIXct(format(Sys.time()-hours(24), format="%Y-%m-%d %H:00:00"), tz="UTC")
enddate <- as.POSIXct(format(Sys.time(), format="%Y-%m-%d %H:00:00"), tz="UTC")

interval <- "PT1H"

```

Choose the parameters and model you want to get and write them in the list. Check here which parameters are available: https://www.meteomatics.com/en/api/available-parameters/

```{r}
parameters <- list("t_2m:C", "dew_point_2m:C", "relative_humidity_2m:p", "precip_1h:mm")
```

Specify the locations for your query
```{r}
postal_code <- list('DE'= c(71679, 70173), 'CH' = c(9014, 9000))
```

In the following, the request will start. If there is an error in the request as for example a wrong parameter or a date that doesn't exist, you get a message.

```{r}
df <- query_special_locations_timeseries (startdate, enddate, interval,
                                                          parameters, username, password,
                                                          postal_code = postal_code,
                                                          on_invalid = "fill_with_invalid")
print(head(df))
```
Now you can use the data for everything you want. For example an overview plot for all stations you queried
```{r}
# Calculate the number of rows and columns based on the unique station IDs
num_stations <- length(unique(df$station_id))
num_cols <- ceiling(num_stations / 4)  # Assuming you want 4 rows
num_rows <- ceiling(num_stations / num_cols)

# Create a new plot with subplots for each station_id
par(mfrow = c(num_rows, num_cols), mar = c(2, 2, 2, 1))
for (station in unique(df$station_id)) {
  # Subset data for the current station_id
  station_data <- subset(df, station_id == station)
  
  # Plot
  plot(station_data$validdate, station_data$`t_2m:C`, type = "l", xlab = "Date", ylab = "Temperature (°C)", main = paste("Station", station), col="black", ylim = c(min(station_data$`dew_point_2m:C`) - 1, max(station_data$`t_2m:C`) + 1))
  lines(station_data$validdate, station_data$`dew_point_2m:C`, col="darkred", type = "l")

  # Add legend
  legend("topright", legend = c("Temperature", "Dew Point"), col = c("black", "darkred"), lty = 1, cex = 0.8)
}

```